\cvsection{Experience}
\begin{cventries}
    \cventry
    {Technical Content Admin}
    {Hackerrank}
    {Work from home}
    {July 2019 - Present}
    {
      \begin{cvitems}
        \item {Managing the external technical content curators for Hackerrank.}
        \item {Creating and testing algorithmic and CS fundamentals based challenges.}
        \item {Exposure: Algorithms and Data Structures, Decision-Making, Problem-Solving}
      \end{cvitems}
    }
  \cventry
    {Intern, Member of Technical Staff (Javascript-Python Team)}
    {D.E. Shaw India Pvt. Ltd.}
    {Hyderabad, India}
    {May 2019 - July 2019}
    {
      \begin{cvitems}
        \item {Implemented an API to suggest the appropriate visualizations of a given data-set.}
        \item {Designed a model to predict relevant field-sets for a given data-set.}
        \item {Developed an algorithm to select the most informative chart type for a given set of fields.}
        \item {Exposure: Highcharts, Jupyter Notebook, Pandas}
      \end{cvitems}
    }
    \cventry
    {Intern, Member of Technical Staff (Cloud Team)}
    {BlueStacks}
    {Gurgaon, India}
    {May 2018 - July 2018}
    {
      \begin{cvitems}
        \item {Implemented an API to translate the text in an image in-place using Google API's and Python Imaging Libraries.}
        \item {Designed a machine learning model to predict if a user would be interested in playing quest.}
        \item {Developed a Google chrome extension to automate population of data store from vendors site.}
        \item {Exposure: Google APIs, AWS, Python Imaging Library(PIL), Chrome Developer Tools, Web Scrapping}
      \end{cvitems}
    }
\end{cventries}
